### 2017-12-10 writing/paper/sections/coincidences.tex
Reviewer 1 comments

We will consider the avoidance sets \(\av{\pi,p}\) where \(\pi\) is a fixed
classical pattern of length 3 and \(p\) is a mesh pattern of length 2 that
varies. The classical pattern \(\pi\) will be called the \emph{dominating
pattern}. Given such a dominating pattern \(\pi\) we will write \(p_1
\coinc{\pi} p_2\) if for the mesh patterns, \(p_1\) and \(p_2\),  the sets
\(\av{\pi,p_1}\) and \(\av{\pi,p_2}\) are equal. If this is the case we say
the two mesh patterns are \emph{coincidenc under} \(\pi\).

@@

\begin{definition}
Let \(p=(\tau,R)\) be a mesh pattern of length \(n\) such that
\(\boks{i,j}\notin R\). We define a mesh pattern \(p^{\boks{i,j}_a} =
(\tau^\prime,R^\prime)\) (\(p^{\boks{i,j}_d}\)) of length \(n+2\) as the pattern
where an ascent (descent) is \emph{inserted} into the box \(\boks{i,j}\) in
\(G(p)\). Formally the new underlying classical pattern is defined by
\begin{equation*}
\tau^\prime(k) = \begin{cases}
    j+t & \text{if } k = i+t,t\in\{1,2\}\\
    \tau(k) & \text{if } \tau(k)\le j \text{ and }k\le i\\
    \tau(k)+2 & \text{if } \tau(k)> j \text{ and }k\le i\\
    \tau(k-2) & \text{if } \tau(k)\le j \text{ and }k> i+2\\
    \tau(k-2)+2 & \text{if } \tau(k)> j \text{ and }k> i+2\\
\end{cases}
\end{equation*}
The ordering of the top branch determines whether an ascent(or descent) is added.
The mesh becomes
\begin{equation*}
\begin{aligned}
R^\prime=&\{\boks{k,\ell}\mid k\le i, \ell\le j, \boks{k,\ell}\in R\} \cup\\
&\{\boks{k,\ell}\mid k\le i, \ell > j, \boks{k,\ell-2}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell \le j, \boks{k-2,\ell}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell > j, \boks{k-2,\ell-2}\in R\}\cup\\
&\{\boks{i+1,j},\boks{i+1,j+1},\boks{i+1,j+2}\}
\end{aligned}
\end{equation*}
\end{definition}
An example of adding an ascent to a mesh pattern can be seen in \FigureRef{fig:adda}.
\begin{figure}
\begin{equation*}
p = \pattern{}{2,3,1}{0/0,1/0,1/3,
                      3/0,3/1,3/3} \quad
p^{\boks{1,1}_a}= \pattern{}{4,2,3,5,1}{0/0,
                        1/0,1/5,
                        2/0,2/1,2/2,2/3,2/5,
                        3/0,3/5,
                        5/0,5/1,5/2,5/3,5/5}
\end{equation*}
\caption{The result of inserting an ascent into
\(p=(231,\{\boks{0,0},\boks{1,0},\boks{1,3},\boks{3,0},\boks{3,1},\boks{3,3}\})\)}
\label{fig:adda}
\end{figure}

@@

\subsection{Coincidence classes of Av(\{231, (12, \textit{R})\}).}
When considering the coincidence classes of
\(\av{\{\perm{2,3,1},\mperm{1,2}{R}\}}\) we first apply the two Dominating
Pattern rules previously established. Starting from \(220\) classes, we result
in \(85 \coinc[(1)]{231}\)-equivalence classes reducing to \(59
\coinc[(2)]{231}\)-equivalence classes, considering mesh patterns with \(12\) as
the underlying classical patterns. However there are fewer
\(\coinc[comp]{231}\)-equivalence classes.

>>>>

We will consider the avoidance sets \(\av{\pi,p}\) where \(\pi\) is a fixed
classical pattern of length 3 and \(p\) is a mesh pattern of length 2 that
varies. The classical pattern \(\pi\) will be called the \emph{dominating
pattern}. Given such a dominating pattern \(\pi\) we will write \(p_1
\coinc{\pi} p_2\) if for the mesh patterns, \(p_1\) and \(p_2\),  the sets
\(\av{\pi,p_1}\) and \(\av{\pi,p_2}\) are equal. If this is the case we say
the two mesh patterns are \emph{coincident under} \(\pi\).

@@

\begin{definition}
Let \(p=(\tau,R)\) be a mesh pattern of length \(n\) such that
\(\boks{i,j}\notin R\). We define a mesh pattern \(p^{\boks{i,j}_a} =
(\tau^\prime,R^\prime)\) (respectively, \(p^{\boks{i,j}_d}\)) of length \(n+2\) as the pattern
where an ascent (respectively descent) is \emph{inserted} into the box \(\boks{i,j}\) in
\(G(p)\). Formally the new underlying classical pattern is defined by
\begin{equation*}
\tau^\prime(k) = \begin{cases}
    j+t & \text{if } k = i+t,t\in\{1,2\}\\
    \tau(k) & \text{if } \tau(k)\le j \text{ and }k\le i\\
    \tau(k)+2 & \text{if } \tau(k)> j \text{ and }k\le i\\
    \tau(k-2) & \text{if } \tau(k)\le j \text{ and }k> i+2\\
    \tau(k-2)+2 & \text{if } \tau(k)> j \text{ and }k> i+2\\
\end{cases}
\end{equation*}
The ordering of the top branch determines whether an ascent(or descent) is added.

The mesh becomes
\begin{equation*}
\begin{aligned}
R^\prime=&\{\boks{k,\ell}\mid k\le i, \ell\le j, \boks{k,\ell}\in R\} \cup\\
&\{\boks{k,\ell}\mid k\le i, \ell > j, \boks{k,\ell-2}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell \le j, \boks{k-2,\ell}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell > j, \boks{k-2,\ell-2}\in R\}\cup\\
&\{\boks{i+1,j},\boks{i+1,j+1},\boks{i+1,j+2}\}
\end{aligned}
\end{equation*}
meaning that the ascent (or descent) is not allowed to be split in the box.
\end{definition}
An example of adding an ascent to a mesh pattern can be seen in \FigureRef{fig:adda}.
\begin{figure}
\begin{equation*}
p = \pattern{}{2,3,1}{0/0,1/0,1/3,
                      3/0,3/1,3/3} \quad
p^{\boks{1,1}_a}= \pattern{}{4,2,3,5,1}{0/0,
                        1/0,1/5,
                        2/0,2/1,2/2,2/3,2/5,
                        3/0,3/5,
                        5/0,5/1,5/2,5/3,5/5}
\end{equation*}
\caption{The result of inserting an ascent into
\(p=(231,\{\boks{0,0},\boks{1,0},\boks{1,3},\boks{3,0},\boks{3,1},\boks{3,3}\})\)}
\label{fig:adda}
\end{figure}

@@

\subsection{Coincidence classes of Av(\{231, (12, \textit{R})\}).}
When considering the coincidence classes of
\(\av{\{\perm{2,3,1},\mperm{1,2}{R}\}}\) we first apply the two Dominating
Pattern rules previously established. Starting from \(220\) classes, we result
in \(85 \coinc[(1)]{231}\)-equivalence classes reducing to \(59
\coinc[(2)]{231}\)-equivalence classes, considering mesh patterns with \(12\) as
the underlying classical patterns. However there are
\(56 \coinc[comp]{231}\)-equivalence classes.

### 2017-12-10 writing/paper/sections/wilf.tex
Reviewer 1 comments

\nextvar[\varfine]
It can be shown by use of the Second Dominating Pattern Rule that the patterns
\textpattern{}{1}{0/0,1/1} and \(q_1 = \textpattern{}{1}{0/0,0/1,1/1}\) are
coincident under \(\perm{2,3,1}\). Consider the decomposition of a non-empty
avoider of \(q_1\) in \(\av{\perm{2,3,1}}\) around the maximum:
\begin{equation*}
    \scriptvar_1 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
This can be explained succinctly by the fact that a permutation containing
\(q_1\) starts with its maximum, and by not allowing the lower-left section of the
\(\perm{2,3,1}\) avoider to be empty we prevent an occurrence from ever
happening.

@@

Similarly to a container of \(m_1\) we will look at the lowest possible
occurrence of \(m_2\), and as before the regions \(A^\prime \et B^\prime\)
together contain an avoider of \(231\) and \(A\) contains a decreasing
subsequence. Since we are considering the lowest occurrence of \(m_2\) the
region \(C^\prime\) does not contain an occurrence of either \(m_2\) or \(231\).

@@

Looking at avoiders of \(\perm{2,3,1}\) and \(m_4\) we
can perform a similar decomposition around the maximum to get
\begin{equation*}
    \scriptvar_4 = \varepsilon \sqcup
    \decompmax{1/0,0/1}{\scriptvar_4}{}{}{\mathcal{\varmaxl}_3}
\end{equation*}
An occurrence of \(m_4\) can never occur in the
top right region. It could only occur between the maximum and the first point
in the region, if and only if this first point is the lowest valued element in
this region, so this top right region must contain a sub-permutation that does not
start with it's minimum, i.e., it is a member of \(\mathcal{\varmaxl}_3 = \av{\av{\textpattern{}{1}{0/0,0/1,1/0}}}\).
Since both \(\mathcal{\varmaxl}_1\) and \(\mathcal{\varmaxl}_3\) have the same
enumeration, \(\scriptvar_3\) and \(\scriptvar_4\) must also have
the same enumeration and are therefore \(m_3\weqv{231}m_4\).

>>>>

\nextvar[\varfine]
It can be shown by use of the Second Dominating Pattern Rule that the patterns
\textpattern{}{1}{0/0,1/1} and \(q_1 = \textpattern{}{1}{0/0,0/1,1/1}\) are
coincident under \(\perm{2,3,1}\). Consider the decomposition of a non-empty
avoider of \(q_1\) in \(\av{\perm{2,3,1}}\) around the maximum:
\begin{equation*}
    \scriptvar_1 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
This can be explained succinctly by the fact that a permutation contains
\(q_1\) if and only if it starts with its maximum, and by not allowing the
lower-left section of the
\(\perm{2,3,1}\) avoider to be empty we prevent an occurrence from ever
happening.

@@

Similarly to a container of \(m_1\) we will look at the lowest possible
occurrence of \(m_2\), and as before the regions \(A^\prime \et B^\prime\)
together contain an avoider of \(231\) and \(A^\prime\) contains a decreasing
subsequence. Since we are considering the lowest occurrence of \(m_2\) the
region \(C^\prime\) does not contain an occurrence of either \(m_2\) or \(231\).

@@

Looking at avoiders of \(\perm{2,3,1}\) and \(m_4\) we
can perform a similar decomposition around the maximum to get
\begin{equation*}
    \scriptvar_4 = \varepsilon \sqcup
    \decompmax{1/0,0/1}{\scriptvar_4}{}{}{\mathcal{\varmaxl}_3}
\end{equation*}
An occurrence of \(m_4\) can never occur entirely within the
top right region, since the maximum is to the left and above any point in this region. It could only occur between the maximum and the first point
in the region, if and only if this first point is the lowest valued element in
this region, so this top right region must contain a sub-permutation that does not
start with it's minimum, i.e., it is a member of \(\mathcal{\varmaxl}_3 = \av{\textpattern{}{1}{0/0,0/1,1/0}}\).
Since both \(\mathcal{\varmaxl}_1\) and \(\mathcal{\varmaxl}_3\) have the same
enumeration, \(\scriptvar_3\) and \(\scriptvar_4\) must also have
the same enumeration and are therefore \(m_3\weqv{231}m_4\).
